Formulating and Validating RDF Constraints Generically

### 2015-01-04 paper/paper 2/paper 2.tex
transformations

\newenvironment{gcotable-1}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
	\begin{center}
  \begin{tabular}{l|l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  \hline

@@

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0.3cm}
	\begin{center}
  \begin{tabular}{r l}

@@

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  \vspace{0.3cm}
	\begin{center}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

@@

\newenvironment{evaluation-generic-overview}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
	\begin{center}
  \begin{tabular}{l|c|c}
  \hline
  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
  \hline

@@

RDF data providers ensure that their data conforms to constraints which are part of the contract between the providers and the consumers of that data.
As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones)\footnote{i.a. Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}.
There is an obvious need to transform a specific constraint (\ms{$sc_{\alpha}$}) (expressed by any constraint language \ms{$\alpha$}) into a specific constraint (\ms{$sc_{\beta}$}) (expressed by any constraint language \ms{$\beta$}) - when they have the same semantics.
We use the RDF-CO as intermediate language for these transformations.
If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from these two specific constraints to the corresponding generic constraint (\ms{gc}),
we can convert them automatically:

@@

We do not need to define mappings for each pair of semantically equivalent specific constraint.
Let's assume we are able to express a constraint by 5/6/7/8/9/10 constraint languages.
Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a specific constraint language
- that are \ms{\( {n \choose 2} \)} mappings for each constraint (example: 10/15/21/28/36/45).
With an intermediate generic constraint, we only need to define \ms{n} mappings from the specific constraints to the generic constraint (example: 5/6/7/8/9/10 ).

@@

First, we map these DL statements to two simple constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):

@@

\tb{ToDO: too much space before and after DL and table environments}

>>>>

\newenvironment{gcotable-1}{
  \scriptsize
  \sffamily
  \vspace{0cm}
  \begin{tabular}{l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
}

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  \hline

@@

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{r l}

@@

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

@@

\newenvironment{evaluation-generic-overview}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|c|c}
  \hline
  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
  \hline

@@

RDF data providers ensure that their data conforms to constraints which are part of the contract between the providers and the consumers of that data.
As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones\footnote{i.a. Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
There is an obvious need to transform a specific constraint (\ms{$sc_{\alpha}$}) (expressed by any constraint language \ms{$\alpha$}) into a specific constraint (\ms{$sc_{\beta}$}) (expressed by any constraint language \ms{$\beta$}) - when they have the same semantics.
We use the RDF-CO as intermediate representation for these transformations.
If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from two equivalent specific constraints to the corresponding generic constraint (\ms{gc}),
we can convert them automatically:

@@

We do not need to define mappings for each pair of semantically equivalent specific constraints.
Let's assume we are able to express a constraint by 5/6/7/8/9/10 constraint languages.
Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a different constraint languages
- that are \ms{\( {n \choose 2} \)} mappings for each constraint (10/15/21/28/36/45 mappings).
With an intermediate generic constraint, we only need to define \ms{n} mappings (one mapping for each specific constraint) from the specific constraints to the generic constraint (5/6/7/8/9/10 mappings).

@@

First, we map these DL statements to two simple generic constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):

@@

\tb{ToDO: too much space before and after DL and table environments}
\tb{ToDo: there are no line breaks for ms environment}
